Motional Ground-State Cooling Outside the Lamb-Dicke Regime

### 2017-07-13 paper.tex
Cooling fitting

%% TODO

Our final cooling results are shown in Fig.~\ref{f-radial} and \ref{f-axial}.
In total, $1000$ cooling pulses (for $100$ ms) are applied along three axes with
cooling begins on the radial second order to remove most energy initially.
To characterize the single atom thermal occupation before and after cooling,
we perform Raman sideband thermometry before and after cooling\fxnote{add citation?}.
For the more tightly confined radial directions (non-degenerate),
we observe clear first-order heating, first-order cooling,
and second-order cooling sidebands before RSC as is shown in red in Figure \ref{f-radial}A.

After cooling, the first and second order cooling sidebands on both radial axes are suppressed.
It is important to note that the simple sideband thermometry formula,
which predicts the ratio of the cooling and heating sideband heights to be $\bar n / (\bar n + 1)$,
assumes that the coupling strength for different motional states to be proportional to $\sqrt{n}$.
Outside of the Lamb-Dickes regime, however,
the coupling strength deviates from this simple scaling rule rapidly
as shown in figure \ref{f-ld}A and since the Raman spectroscopy is performed
with a relatively large Raman Lamb-Dickes parameters $\eta^R$, we cannot use this formula to
measure $\bar n$. Instead, given the absence of the second order cooling sideband,
we assume that the atoms are cold enough to have stronger coupling to the first order cooling
sideband than the second order, in which case the

\fxnote{How is the thermometry done? pulse duration etc.}
, we perform sideband thermometry
by taking the ratio of the peaks of first-order cooling and heating sidebands to measure $\bar n / (\bar n + 1)$ \fxnote{cite}.
We found $\{\bar n =,\bar n =\}$, which corresponds to a ground state population of $90(2)$\%
and $94(3)$\% along the two radial directions.

we therefore use an independent measurement of Rabi flopping on the carrier (Fig. \ref{f-radial}B)
and first-order heating(Fig. \ref{f-radial}C) sidebands
to verify the ground-state population~\cite{Meekhof1996}.
The data is fitted using the same Monte-Carlo simulation we used to simulate the cooling
which yields $89(2)$\% and $92(2)$\% and show good agreement with
the population extracted from the sideband thermometry.
We also extracted the initial temperature before cooling
from the motional-state decohered Rabi flopping and obtained $70 \mu$K.

%% End of TODO

>>>>

Our final cooling results are shown in Fig.~\ref{f-radial} and \ref{f-axial}.
In total, $1000$ cooling pulses (for $100$ ms) are applied along three axes with
cooling begins on the radial second order to remove most energy initially.
To characterize the single atom thermal occupation before and after cooling,
we perform Raman sideband thermometry before and after cooling.
For the more tightly confined radial directions (non-degenerate),
we observe clear first-order heating, first-order cooling,
and second-order cooling sidebands before RSC as is shown in red in Figure \ref{f-radial}A.
After cooling, the first and second order cooling sidebands on both radial axes are suppressed.
It is important to note that the simple sideband thermometry formula,
which predicts the ratio of the cooling and heating sideband heights
to be $\bar n / (\bar n + 1)$~\cite{Monroe1995},
assumes that the coupling strength for different motional states to be proportional to $\sqrt{n}$.
Outside of the Lamb-Dickes regime, however,
the coupling strength deviates from this simple scaling rule rapidly
as shown in figure \ref{f-ld}A and since the Raman spectroscopy is performed
with a relatively large Raman Lamb-Dickes parameters $\eta^R$, we cannot use this formula to
measure $\bar n$.
Instead, given the absence of the second order cooling sideband,
we assume that the atoms are cold enough to have stronger coupling to the first order cooling
sideband than the second order, in which case the lower bound of the ground state population
can be computed from the heights of the sidebands by assuming all of the excitation are in the
$n=1$ state. In doing this, we found a ground state population of $90(2)$\%
and $94(3)$\% along the two radial directions.
We also use an independent measurement of Rabi flopping on the carrier (Fig. \ref{f-radial}B)
and first-order heating(Fig. \ref{f-radial}C) sidebands
to verify the ground-state population~\cite{Meekhof1996}.
The data is fitted using the same Monte-Carlo simulation we used to simulate the cooling
which yields $89(2)$\% and $92(2)$\% and show good agreement with
the population extracted from the sideband thermometry.
We also extracted the initial temperature before cooling
from the motional-state decohered Rabi flopping and obtained $70 \mu$K.
